Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-07 code.tex
Updates from ShareLaTeX

 def __init__(i,x,y):
    if x.score < y.score:
      x,y = y,x      # x must have best score
    i.c = dist(x,y) 
    i.obj = len(x) 
    Line.all += [i]  # remember this line

>>>>

 def __init__(i,x,y):
    if x.score < y.score:
      x,y = y,x      # x must have best score
    i.x, i.y, i.c = x, y, dist(x,y) 
    i.obj = len(x) 
    Line.all += [i]  # remember this line
